hbm_paper_results

### 2024-02-16 paper_main_results.Rmd

```{r}
centile.t.tests(diffs.df, feature_list=pheno_abs.diff.list) #testing abs(error)
```

@@

get stat results for global phenos:
```{r, message=FALSE}
full_cent_res <- centile.t.tests.full_result(diffs.df, feature_list=pheno_abs.diff.list)
full_cent_res %>%
  dplyr::filter(pheno %in% vol_list_global) %>%
  dplyr::filter(!grepl('_refA', comp))
```

@@

centile error diffs
```{r, message=FALSE}
centile.t.tests(no_ext, feature_list=pheno_abs.diff.list)
```

@@

```{r}
centile.t.tests(diffs.df, feature_list=z.pheno_abs.diff.list)
```

@@

z error diffs
```{r}
centile.t.tests(z.no_ext, feature_list=z.pheno_abs.diff.list)
```

>>>>

```{r}
full_cent_res <- centile.t.tests.full_result(diffs.df, feature_list=pheno_abs.diff.list)
full_cent_res %>%
  group_by(comp, bigger_group) %>%
  summarize(n_sig_regions = sum(sig_fdr),
            min_pval=min(p.val_fdr),
            max_pval=max(p.val_fdr)) %>%
  dplyr::filter(!grepl('_refA', comp))#drop refA levels
```

```{r, eval=FALSE}
full_cent_res%>%
  dplyr::filter(comp =="cf.gamlss_cf" & bigger_group == "cf.gamlss" & sig_fdr ==TRUE)

diffs.df %>%
  dplyr::filter(dataset=="cf.gamlss" | dataset =="cf") %>%
  ggplot() +
  geom_boxplot(aes(y=abs.diff_rh_CT_parstriangularis, fill=dataset))

diffs.df %>%
  dplyr::filter(dataset=="cf.gamlss" | dataset =="cf") %>%
  ggplot() +
  geom_boxplot(aes(y=diff_rh_CT_parstriangularis, fill=dataset))
```

@@

get stat results for global phenos:
```{r, message=FALSE}
full_cent_res %>%
  dplyr::filter(pheno %in% vol_list_global) %>%
  dplyr::filter(!grepl('_refA', comp))

full_cent_res %>%
  dplyr::filter(bigger_group == "cf.gamlss")%>%
  dplyr::filter(!grepl('_refA', comp))
```

@@

centile error diffs
```{r}
noext_cent_res <- centile.t.tests.full_result(no_ext, feature_list=pheno_abs.diff.list)
noext_cent_res %>%
  group_by(comp, bigger_group) %>%
  summarize(n_sig_regions = sum(sig_fdr),
            min_pval=min(p.val_fdr),
            max_pval=max(p.val_fdr)) %>%
  dplyr::filter(!grepl('_refA', comp))#drop refA levels
```

@@

```{r}
full_z_res <- centile.t.tests.full_result(diffs.df, feature_list=z.pheno_abs.diff.list)
full_z_res %>%
  group_by(comp, bigger_group) %>%
  summarize(n_sig_regions = sum(sig_fdr),
            min_pval=min(p.val_fdr),
            max_pval=max(p.val_fdr)) %>%
  dplyr::filter(!grepl('_refA', comp))#drop refA levels
```

@@

z error diffs
```{r}
noext_z_res <- centile.t.tests.full_result(z.no_ext, feature_list=z.pheno_abs.diff.list)
noext_z_res %>%
  group_by(comp, bigger_group) %>%
  summarize(n_sig_regions = sum(sig_fdr),
            min_pval=min(p.val_fdr),
            max_pval=max(p.val_fdr)) %>%
  dplyr::filter(!grepl('_refA', comp))#drop refA levels
```
